---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Withr - Run Code 'With' Modified State #
[![Travis-CI Build Status](https://travis-ci.org/jimhester/withr.svg?branch=master)](https://travis-ci.org/jimhester/withr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/jimhester/withr?branch=master&svg=true)](https://ci.appveyor.com/project/jimhester/withr)
[![Coverage Status](https://img.shields.io/codecov/c/github/jimhester/withr/master.svg)](https://codecov.io/github/jimhester/withr?branch=master)

A set of functions to run code 'with' safely and temporarily modified global
state.

Many of these functions were originally a part of the [devtools][] package,
this provides a simple package with limited dependencies to provide access to
these functions.

- with_collate - collation order
- with_dir - working directory
- with_envvar - environment variables
- with_libpaths - library paths
- with_locale - any locale setting
- with_makevars - Makevars variables
- with_options - options
- with_par - graphics parameters
- with_path - PATH environment variable

There is also a `with_()` function to construct new `with_*` functions if
needed.

```{r}
getwd()
with_dir(tempdir(), getwd())
getwd()

Sys.getenv("HADLEY")
with_envvar(c("HADLEY" = 2), Sys.getenv("HADLEY"))
Sys.getenv("HADLEY")

with_envvar(c("A" = 1),
  with_envvar(c("A" = 2), action = "suffix", Sys.getenv("A"))
)
```
# See Also #
- [Devtools][devtools]

[devtools]: https://github.com/hadley/devtools
