---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
knitr::opts_knit$set(root.dir = tempdir())
```

# Withr - Run Code 'With' Modified State #
[![Travis-CI Build Status](https://travis-ci.org/jimhester/withr.svg?branch=master)](https://travis-ci.org/jimhester/withr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/jimhester/withr?branch=master&svg=true)](https://ci.appveyor.com/project/jimhester/withr)
[![Coverage Status](https://img.shields.io/codecov/c/github/jimhester/withr/master.svg)](https://codecov.io/github/jimhester/withr?branch=master)
[![CRAN Version](http://www.r-pkg.org/badges/version/withr)](http://www.r-pkg.org/pkg/withr)

A set of functions to run code 'with' safely and temporarily modified global
state. There are two sets of functions, those prefixed with `with_` and those
with `local_`. The former reset their state as soon as the `code` argument has
been evaluated. The latter reset when they reach the end of their scope,
usually at the end of a function body.

Many of these functions were originally a part of the [devtools][] package,
this provides a simple package with limited dependencies to provide access to
these functions.

- `with_collate()` / `local_collate()` - collation order
- `with_dir()` / `local_dir()` - working directory
- `with_envvar()` / `local_envvar()` - environment variables
- `with_libpaths()` / `local_libpaths()` - library paths
- `with_locale()` / `local_locale()` - any locale setting
- `with_makevars()` / `local_makevars()` - Makevars variables
- `with_options()` / `local_options()` - options
- `with_par()` / `local_par()` - graphics parameters
- `with_path()` / `local_path()` - PATH environment variable

There are also `with_()` and `local_()` functions to construct new `with_*`
and `local_*` functions if needed.

```{r}
dir.create("test")
getwd()
with_dir("test", getwd())
getwd()
unlink("test")

Sys.getenv("HADLEY")
with_envvar(c("HADLEY" = 2), Sys.getenv("HADLEY"))
Sys.getenv("HADLEY")

with_envvar(c("A" = 1),
  with_envvar(c("A" = 2), action = "suffix", Sys.getenv("A"))
)
```

# See Also #
- [Devtools][devtools]

[devtools]: https://github.com/hadley/devtools
